invivoPKfit analysis of CvTdb data

### 2023-01-11 Working Rmds/MainAnalysis.Rmd
Do and save postprocessing of flat model output
Now each study has its own SD, where study = chemical + species + reference + route + media

```{r}
defaults_list <- list(
                      "Weight.Units" = "kg",
                      "Dose.Units" = "mg/kg",
                      "Time.Units" = "h",
                      "Value.Units" = "mg/L")
```

@@

rm(PK.fit.table.flat)
```

@@

```{r, run_invivoPKfit_1comp}

### do 1-Compartment fit
system.time(
    PK.fit.table.1comp <- fit_all(
      data.set = cvt,
      model = "1compartment",
      modelfun = "analytic",
      preprocess = FALSE,
      optimx_args = list(
                      "method" = "bobyqa",
                      "itnmax" = 1e6,
                      "control" = list("kkt" = FALSE)
                    ),
      suppress.messages = TRUE
  )
)

>>>>

```{r}
defaults_list <- list(
                      "Weight.Units" = "kg",
                      "Dose.Units" = "mg/kg",
                      "Time.Units" = "hours",
                      "Value.Units" = "mg/L")
```

@@

post_flat <- postprocess_data(PK_fit = PK.fit.table.flat,
                               model = "flat")

write.csv(post_flat,
          paste("../inst/ext/PK_fit_postprocess_flat_",
                                    timestamp,
                                    ".csv",
                                    sep=""),
          row.names = FALSE)

rm(PK.fit.table.flat, post_flat)
```

@@

```{r, run_invivoPKfit_1comp}
### do 1-Compartment fit
system.time(
    PK.fit.table.1comp <- fit_all(
      data.set = cvt,
      model = "1compartment",
      modelfun = "analytic",
      preprocess = FALSE,
      optimx_args = list(
                      "method" = "bobyqa",
                      "itnmax" = 1e6,
                      "control" = list("kkt" = FALSE)
                    ),
      suppress.messages = TRUE
  )
)
